
  This chapter includes the conclusion and provides an outlook for future
  research.

  \section{Conclusion}
  \label{section:conclusion}

  The aim of this thesis was to assess to what extent semi-synthetic graphs 
  are useful for gaining customer insights using \acs{gml}. This aim corresponds 
  to the research question stated in section \ref{section:research_topics}. The
  results for answering this question are mixed and are based on the data
  presented in chapter \ref{section:data}, the results of chapter
  \ref{section:results}, and the discussion in chapter \ref{section:discussion}.
  \\

  \noindent \acs{gml} on the network created from the bank telemarketing dataset 
  fails to overcome the problem of unbalanced labels. It however yields similar 
  results in terms of accuracy as the standard \acs{ml} models. In addition it 
  is shown, that if a network structure can be created which corresponds to the 
  label, that the problem of unbalanced label data could be overcome. \\

  \noindent GraphSage performs well for the \acs{us} airline passenger dataset 
  and is second only to the random forest classifier in terms of accuracy. As
  discussed, following the principle of Occam's razor, the good results for the
  GraphSage model must be taken with a grain of salt. For the purpose of
  gaining customer insights, simpler models such as \acsp{ann}, \acsp{svm}, and 
  AdaBoost provide only marginally inferior results and are more practical and 
  thus preferable for this setting. Given similar results for more sensitive 
  applications in fields such as medicine, the GraphSage model could be 
  preferred as even marginal performance improvements can be of utmost importance. 
  In short, the GraphSage yields competitive results in terms of accuracy, 
  the results are however not superior enough to necessarily warrant the complex 
  graph generation process and model complexity of GraphSage. Lastly, the 
  \acs{gcn} and Node2Vec are not successful for the given classification task. 
  For that reason, more recent \acs{gml} models should be tested and/or new 
  models should be developed to expand the possibilities of \acs{gml}.\\

  \noindent The perhaps most interesting result is provided by the \acs{us} 
  airline passenger graph plots shown in figure \ref{fig:us_airline_nodes}. The 
  \acs{mag} model successfully generated neighborhoods within the graph, where 
  the nodes are grouped according to their similarity which respects the 
  similarities between all attributes. This observation is further confirmed 
  by the scatterplots shown in figure \ref{fig:node2vec}. The graphs and the 
  scatterplots make it possible to visually interpret the relationships within 
  the data. Standard scatterplots using the feature data do not allow for the 
  generation of such insightful graphs/plots. \\

  \noindent To summarize and provide an answer to the research question, it is
  shown that yes, semi-synthetic graphs can be useful for \acs{gml} in a
  classification setting. The \acs{gml} models are shown to be competitive and 
  could potentially even provide a solution for overcoming the difficulties 
  associated with unbalanced label data. This however requires the availability 
  of a graph with a structure which corresponds to the label. The usefulness of 
  semi-synthetic graphs are limited by the complexity associated with generating 
  graphs and the general complexity of the \acs{gml} models. In addition, the
  network properties of the \acs{mag} is a limiting factor for the \acs{gml}
  models. The graph based models further fail to outperform the standard 
  \acs{ml} models and are ranked anywhere between the second to fifth best model 
  depending on how one weights the trade-off between model complexity and accuracy. 
  Based on this, the hypotheses presented in section 
  \ref{section:research_topics} can be answered as follows: \\

  \noindent\textbf{H1:} Graph machine learning models using semi-synthetic graphs 
  fail to outperform standard machine learning modelss. This hypothesis is thus
  rejected. \\

  \noindent\textbf{H2:} Graph machine learning is shown to be a competitive
  strategy with competitive results in line with the results shown for the
  standard machine learning models. This hypothesis is not rejected.

  \section{Outlook}

  The discussion in chapter \ref{section:discussion} and the conclusion in section
  \ref{section:conclusion} provides interesting topics for future research.
  These topics include graph generation, cluster analysis on graphs, and
  \acs{gml} models and are presented in the following paragraphs.
  \newpage
  \paragraph{Graph Generation} \mbox{}
  
  \noindent Creating semi-synthetic graphs using the \acs{mag} model is shown to 
  be a viable approach. The graph is however sensitive to attribute selection and 
  setting appropriate link-affinity probabilities. A fist step for resolving
  this issue was introduced by \cite{kim2011modeling} as a follow up to their
  \acs{mag} model. In this paper they propose a reverse model, in which given a real
  graph, the attributes and the link-affinity probabilities are estimated such 
  that the attributes and link-affinity probabilities generate the observed real
  graph. This is however only a partial solution to the task given for this
  master's thesis. The estimated attributes do not correspond to real 
  attributes/features. In this model, the attributes are estimated to fit the 
  graph. An interesting topic for future research would be to develop a model 
  that generates a semi-synthetic graph based on real attributes which at the same
  time optimizes the link-affinity probabilities such that the resulting graph
  adheres to real network properties. Perhaps these more realistic graph 
  properties can improve the performance for \acs{gml}. This is an area worth 
  consideration as especially the degree distribution and centrality measures 
  shown in figure \ref{fig:centrality_measures} force \acs{gml} models to 
  consider a large number of neighbors. In addition even when sampling, the 
  neighborhood is bound to always have the same size given the range of the 
  degree distribution shown in figure \ref{fig:centrality_measures}. This is a
  potentially serious limiting factor for \acs{gml}, as it makes it more difficult to 
  distinguish between more local structures within the graph.

  \paragraph{Cluster Analysis on Graphs} \mbox{}

  \noindent The graph plots shown in figure \ref{fig:us_airline_nodes} reveal,
  that \acsp{mag} can be excellent tools for visualizing data. The
  amount of useful information provided for interpreting the data is a welcome
  and unexpected result. For understanding the relationships between the
  attribute data and the label, the graph plots yielded the most useful
  information for identifying relationships within the data. An interesting
  topic for future research could be to assess how common clustering models
  such as k-means, fuzzy clustering or CLIQUE could be used for analyzing
  graphs. Perhaps better and more graph centric models could be developed. An
  excellent overview of existing graph clustering models is provided by
  \cite{zhou2020graph}. Their article can be used as an initial reference point
  for identifying new applications of existing graph clustering methods or for 
  developing new models.

  \paragraph{Graph Machine Learning Models}\mbox{}

  \noindent \acsp{gcn} and GraphSage were selected for this master's thesis as 
  they are probably the two most well-known \acsp{gnn}. There are however 
  newer and more sophisticated models such as \acp{gat} \citep{velivckovic2018graph} 
  or \acp{gin} \citep{xu2019powerful}. \\

  \noindent \acs{gat} models have the ability of identifying more- or less 
  important neighbors in the graph. This is a useful ability and has been shown 
  to improve performance in some cases. This ability is unfortunately most likely 
  limited by the very large number of vertex degrees present in the \acs{us} 
  airline passenger graph as shown in figure \ref{fig:centrality_measures}. For 
  that reason, more realistic graphs with smaller number of degrees should be
  generated as discussed in section \ref{section:comp_disc}. \\

  \noindent \acs{gin} models are very well suited for distinguishing structures 
  within the graph. The authors \cite{xu2019powerful} present the general
  \acs{gin} framework which can accept any type of features as inputs whilst 
  ensuring that the aggregation function is injective. Given the injective 
  aggregation strategy, it is shown that the \acs{gin} can be as powerful at 
  distinguishing graph structures as the Weisfeiler-Lehman graph isomorphism test 
  \citep{weisfeiler1968}. Again, for such a model to work best, the number of
  degrees would most likely need to be smaller than currently present in the
  graph of the \acs{us} airline passenger dataset. Given the large number of 
  degrees, the neighborhoods of every node are currently of the same size when 
  using the sampling strategy outlined for the GraphSage model. \\

  \noindent Given a more realistic graph with a smaller number of degrees, it
  would be interesting to develop and assess, whether a new model which
  includes the attention mechanism of the \acs{gat} and the isomorphic 
  capabilities of the \acs{gin} could be of use. This new model could for
  instance then be tested on well understood benchmark graphs such as Cora
  \citep{mccallum2000automating} or Citeseer \citep{giles1998citeseer}. 

